```{r}
library(caret)
```

```{r}
set.seed(100)
curDir <- '/Users/aakef/Documents/School/csp571/DataPrepProject'
setwd(curDir)
#library(ggplot2)
library(tidyverse)
data.raw1 <- read.csv(file='dataset-of-00s.csv')
data.raw2 <- read.csv(file='dataset-of-10s.csv')
data.raw3 <- read.csv(file='dataset-of-60s.csv')
data.raw4 <- read.csv(file='dataset-of-70s.csv')
data.raw5 <- read.csv(file='dataset-of-80s.csv')
data.raw6 <- read.csv(file='dataset-of-90s.csv')

#Combine all data sorces together
data.raw <- ( rbind(data.raw1,data.raw2) %>% rbind(data.raw3) %>% rbind(data.raw4)
  %>% rbind(data.raw5) %>% rbind(data.raw6) )
```

```{r}
class(data.raw)
dim(data.raw)
str(data.raw)

#Check entire table for NA values
table(is.na(data.raw))
#See where NA values lies
colSums(is.na(data.raw))
#Omit NA values
data.raw1<-na.omit(data.raw)
#Get the summary of the dataset
summary(data.raw)
#Remove unnecessary columns
data.raw<-data.raw %>% select(-c(track,artist,uri))
```

```{r}
data.raw$target
```

```{r}
trainIndex <- createDataPartition(data.raw$target, times=1, p=0.8, list=FALSE)
train <- data.raw[trainIndex,]
test <- data.raw[-trainIndex,]
fitted <- glm(target~., data=data.raw, family = "binomial")
```

```{r}
summary(fitted)[["coefficients"]]
```

Danceability and Speechiness seem to most correlated with a song being a hit across time

```{r}
probs <- predict(fitted,newdata=test, type = "response")
preds <- ifelse(probs > 0.5, 1, 0)
actuals = as.integer(test$target == 1, 1, 0)
confusionMatrix(data=as.factor(preds), reference=as.factor(actuals))
```

![]()

Using all the variables we get a 72% accuracy

Let's try retraining the model with variables that only got coeeficients \>= \|1\|

```{r}
trainIndex <- createDataPartition(data.raw$target, times=1, p=0.8, list=FALSE)
train <- data.raw[trainIndex,]
test <- data.raw[-trainIndex,]
fitted_some <- glm(target~danceability+energy+speechiness+acousticness+instrumentalness, data=data.raw, family = "binomial")

probs <- predict(fitted_some,newdata=test, type = "response")
preds <- ifelse(probs > 0.5, 1, 0)
actuals = as.integer(test$target == 1, 1, 0)
confusionMatrix(data=as.factor(preds), reference=as.factor(actuals))
```

We get a slightly lower accuracy using a third of the features

```{r}
#data.raw3<-data.raw3 %>% select(-c(track,artist,uri))
trainIndex6 <- createDataPartition(data.raw3$target, times=1, p=0.8, list=FALSE)
train6 <- data.raw3[trainIndex6,]
test6 <- data.raw3[-trainIndex6,]
fitted6 <- glm(target~., data=data.raw3, family = "binomial")

```

```{r}
summary(fitted6)[["coefficients"]]
```

Speechiness was a lot more valued in the 60s

```{r}
probs <- predict(fitted6,newdata=test, type = "response")
preds <- ifelse(probs > 0.5, 1, 0)
actuals = as.integer(test$target == 1, 1, 0)
confusionMatrix(data=as.factor(preds), reference=as.factor(actuals))
```

```{r}
#data.raw2<-data.raw2 %>% select(-c(track,artist,uri))
trainIndex10 <- createDataPartition(data.raw2$target, times=1, p=0.8, list=FALSE)
train10 <- data.raw2[trainIndex10,]
test10 <- data.raw2[-trainIndex10,]
fitted10 <- glm(target~., data=data.raw2, family = "binomial")
```

```{r}
summary(fitted10)[["coefficients"]]
```

In the 2010s dancebility and energy are a lot more popular than in the 60s

```{r}
probs <- predict(fitted10,newdata=test, type = "response")
preds <- ifelse(probs > 0.5, 1, 0)
actuals = as.integer(test$target == 1, 1, 0)
confusionMatrix(data=as.factor(preds), reference=as.factor(actuals))
```
