---
title: "Spotify Hits Prediction"
output: html_notebook
---

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

'<https://rstudio-pubs-static.s3.amazonaws.com/594440_b5a14885d559413ab6e57087eddd68e6.html>' '<https://docs.google.com/document/d/1i92D1-matJAphxoDAnobR28NwUT9rPpEPlZirv_4JpA/edit#heading=h.ijf9odsaw24a>'

```{r}
set.seed(100)
curDir <- '/home/tinhc/Documents/GitHub/DataPrepProject'
setwd(curDir)
#library(ggplot2)
library(tidyverse)
data.raw1 <- read.csv(file='dataset-of-00s.csv')
data.raw2 <- read.csv(file='dataset-of-10s.csv')
data.raw3 <- read.csv(file='dataset-of-60s.csv')
data.raw4 <- read.csv(file='dataset-of-70s.csv')
data.raw5 <- read.csv(file='dataset-of-80s.csv')
data.raw6 <- read.csv(file='dataset-of-90s.csv')

#Combine all data sorces together
data.raw <- ( rbind(data.raw1,data.raw2) %>% rbind(data.raw3) %>% rbind(data.raw4)
  %>% rbind(data.raw5) %>% rbind(data.raw6) )
```

```{r}
class(data.raw)
dim(data.raw)
str(data.raw)

#Check entire table for NA values
table(is.na(data.raw))
#See where NA values lies
colSums(is.na(data.raw))
#Omit NA values
data.raw1<-na.omit(data.raw)
#Get the summary of the dataset
summary(data.raw)
#Remove unnecessary columns
data.raw<-data.raw %>% select(-c(track,artist,uri))
```

Compute the correlation matrix

```{r}
library(ggcorrplot)
corr <- round(cor(data.raw),2)

#Calculate the corelation between p-value
pmat <- cor_pmat(data.raw)
head(pmat)

head(corr)
#Visualize the correlation matrix
ggcorrplot(corr)
#Reduce the correlation matrix to keep only lower half with hierarchical order
ggcorrplot(corr, hc.order = TRUE, type = "lower",
     outline.col = "white")
```

```{r}
# Add correlation significance level
# Check-mark the no significant coefficient features based on p-value
ggcorrplot(corr, method='circle', hc.order = TRUE,
    type = "lower", p.mat = pmat)
```

Now, we will explore some of the key features against our target value

```{r}
#Plot of top hit with duration.
ggplot(data=data.raw,title='Correlation Matrix')+
  geom_histogram(aes(x=duration_ms, fill="red"), binwidth  = 1000)+
  ggtitle('Histogram distribution of Duration (ms)')  + 
  labs(y = "Count", x = "Duration (ms)")
```

Let see our distribution between energy and target

```{r}
#We have a Generalized Addictive Model (GAM) smoothing function here to see 
#whether energy 
ggplot(data = data.raw) + 
  geom_point(mapping = aes(x = energy, y = target)) +
  geom_smooth(mapping = aes(x = energy, y = target),method='gam')
```

Notice that we have duration and section pair are perfectly correlated, as well as energy and loudness. For a song to be longer, it will naturally contains more sections inside. The correlation between energy and loudness is also very common because a higher peak in energy will deliver a higher energy spectrum. Hence, we propose another set of data that drops duration and loudness.

```{r}
#Remove duration and loudness from our dataset. Called it dataset.adj
data.adj<-data.raw %>% select(-c(duration_ms,loudness))
```

Now, we will use reticulate library, which will have an embedded pthon environment in R, to plot our variable.

```{r}
library(reticulate)
use_python('/home/tinhc/anaconda3/bin/python')
#importing required Python libraries/modules
sns <- import('seaborn')
plt <- import('matplotlib.pyplot')
pd <- import('pandas')

#building a seaborn pairplot using pairplot() part 1
sns$pairplot(r_to_py(data.adj %>% select(c(danceability,energy,key,target))), hue = 'target')
#display the plot
plt$gcf()$set_size_inches(3, 4)
plt$tight_layout()
plt$show()
plt$close('all')
```

```{r}
#building a seaborn pairplot using pairplot() part 2
sns$pairplot(r_to_py(data.adj %>% select(c(mode,speechiness,acousticness,target))), hue = 'target')
#display the plot
plt$gcf()$set_size_inches(3, 4)
plt$tight_layout()
plt$show()
plt$close('all')
```

```{r}
#building a seaborn pairplot using pairplot() part 3
sns$pairplot(r_to_py(data.adj %>% select(c(instrumentalness,liveness,valence,target))), hue = 'target')
#display the plot
plt$gcf()$set_size_inches(3, 4)
plt$tight_layout()
plt$show()
plt$close('all')
```

```{r}
#building a seaborn pairplot using pairplot() part 4
sns$pairplot(r_to_py(data.adj %>% select(c(valence,tempo,time_signature,target))), hue = 'target')
#display the plot
plt$gcf()$set_size_inches(3, 4)
plt$tight_layout()
plt$show()
plt$close('all')
```

```{r}
#building a seaborn pairplot using pairplot() part 5
sns$pairplot(r_to_py(data.adj %>% select(c(chorus_hit,sections,target))), hue = 'target')
#display the plot
plt$gcf()$set_size_inches(3, 4)
plt$tight_layout()
plt$show()
plt$close('all')
```
