---
title: "Spotify Hits Prediction"
output: html_notebook
---

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

'<https://rstudio-pubs-static.s3.amazonaws.com/594440_b5a14885d559413ab6e57087eddd68e6.html>' '<https://docs.google.com/document/d/1i92D1-matJAphxoDAnobR28NwUT9rPpEPlZirv_4JpA/edit#heading=h.ijf9odsaw24a>'

```{r}
set.seed(100)
curDir <- '/home/tinhc/Documents/GitHub/DataPrepProject'
setwd(curDir)
#library(ggplot2)
library(tidyverse)
data.raw1 <- read.csv(file='dataset-of-00s.csv')
data.raw2 <- read.csv(file='dataset-of-10s.csv')
data.raw3 <- read.csv(file='dataset-of-60s.csv')
data.raw4 <- read.csv(file='dataset-of-70s.csv')
data.raw5 <- read.csv(file='dataset-of-80s.csv')
data.raw6 <- read.csv(file='dataset-of-90s.csv')

#Combine all data sorces together
data.raw <- ( rbind(data.raw1,data.raw2) %>% rbind(data.raw3) %>% rbind(data.raw4)
  %>% rbind(data.raw5) %>% rbind(data.raw6) )
```

```{r}
class(data.raw)
dim(data.raw)
str(data.raw)

#Check entire table for NA values
table(is.na(data.raw))
#See where NA values lies
colSums(is.na(data.raw))
#Omit NA values
data.raw<-na.omit(data.raw)
#Get the summary of the dataset
summary(data.raw)
#Remove unnecessary columns
data.raw<-data.raw %>% select(-c(track,artist,uri))
```

Compute the correlation matrix

```{r}
library(ggcorrplot)
corr <- round(cor(data.raw),2)

#Calculate the corelation between p-value
pmat <- cor_pmat(data.raw)
head(pmat)

head(corr)
#Visualize the correlation matrix
ggcorrplot(corr)
#Reduce the correlation matrix to keep only lower half with hierarchical order
ggcorrplot(corr, hc.order = TRUE, type = "lower",
     outline.col = "white")+
  labs(title='Correlation matrix of our features')
```

```{r}
# Add correlation significance level
# Check-mark the no significant coefficient features based on p-value
ggcorrplot(corr, method='circle', hc.order = TRUE,
    type = "lower", p.mat = pmat)+
  ggtitle('Correlation matrix with p-value significant cross out')
```

Now, we will explore some of the key features against our target value

```{r}
#Plot of top hit with duration.
ggplot(data=data.raw,title='Correlation Matrix')+
  geom_histogram(aes(x=duration_ms, fill="red"), binwidth  = 1000)+
  ggtitle('Histogram distribution of Duration (ms)')  + 
  labs(y = "Count", x = "Duration (ms)")
```

Let see our distribution between energy and target

```{r}
#We have a Generalized Addictive Model (GAM) smoothing function here to see 
#whether energy 
ggplot(data = data.raw) + 
  geom_point(mapping = aes(x = energy, y = target)) +
  geom_smooth(mapping = aes(x = energy, y = target),method='gam') +
  ggtitle('Distribution between energy and target')
```

Notice that we have duration and section pair are perfectly correlated, as well as energy and loudness. For a song to be longer, it will naturally contains more sections inside. The correlation between energy and loudness is also very common because a higher peak in energy will deliver a higher energy spectrum. Hence, we propose another set of data that drops duration and loudness.

```{r}
#Remove duration and loudness from our dataset. Called it dataset.adj
data.adj<-data.raw %>% select(-c(duration_ms,loudness))
```
Using R code to plot pairwise charts
```{r}
library(GGally)
pairplot1<-ggpairs(data.adj, 
        columns = c('danceability','energy','key'),
        aes(color= target, alpha = 0.5),
        upper = list(continuous = wrap("density", alpha = 0.5), combo = "box"),
        lower = list(continuous = wrap("points", alpha = 0.3), combo = wrap("dot", alpha = 0.4)),
        diag = list(continuous = wrap("densityDiag")),
        title = "Pair plot between features")+
        scale_fill_manual(values=c('0'="#509BF5", '1'= "#EB1E32"))
pairplot1
```


Now, we will use reticulate library, which will have an embedded pthon environment in R, to plot our variable.I

```{r}
pairplot2<-ggpairs(data.adj, 
        columns = c('mode','speechiness','acousticness'),
        aes(color= target, alpha = 0.5),
        upper = list(continuous = wrap("density", alpha = 0.5), combo = "box"),
        lower = list(continuous = wrap("points", alpha = 0.3), combo = wrap("dot", alpha = 0.4)),
        diag = list(continuous = wrap("densityDiag")),
        title = "Pair plot between features")+
        scale_fill_manual(values=c('0'="#509BF5", '1'= "#EB1E32"))
pairplot2
```

```{r}
pairplot3<-ggpairs(data.adj, 
        columns = c('instrumentalness','liveness','valence'),
        aes(color= target, alpha = 0.5),
        upper = list(continuous = wrap("density", alpha = 0.5), combo = "box"),
        lower = list(continuous = wrap("points", alpha = 0.3), combo = wrap("dot", alpha = 0.4)),
        diag = list(continuous = wrap("densityDiag")),
        title = "Pair plot between features")+
        scale_fill_manual(values=c('0'="#509BF5", '1'= "#EB1E32"))
pairplot3
```


```{r}
pairplot4<-ggpairs(data.adj, 
        columns = c('tempo','chorus_hit','sections'),
        aes(color= target, alpha = 0.5),
        upper = list(continuous = wrap("density", alpha = 0.5), combo = "box"),
        lower = list(continuous = wrap("points", alpha = 0.3), combo = wrap("dot", alpha = 0.4)),
        diag = list(continuous = wrap("densityDiag")),
        title = "Pair plot between features")+
        scale_fill_manual(values=c('0'="#509BF5", '1'= "#EB1E32"))
pairplot4
```

```{r}
```
Now, we will explore how some characteristics of the song over time. To do it, we need to create a dummy variable that represent times as our original dataset does not have such features.
```{r}
library(fastDummies)
yr00 <- dummy_cols(data.raw1,select_columns="target",remove_first_dummy = TRUE)
colnames(yr00)[20] <- "year"
yr00$year[yr00$year == 0||yr00$year==1 ] <- '2000' 

yr10 <- dummy_cols(data.raw2,select_columns="target",remove_first_dummy = TRUE)
colnames(yr10)[20] <- "year"
yr10$year[yr10$year == 0||yr10$year==1 ] <- '2010' 

yr60 <- dummy_cols(data.raw3,select_columns="target",remove_first_dummy = TRUE)
colnames(yr60)[20] <- "year"
yr60$year[yr60$year == 0||yr60$year==1 ] <- '1960'

yr70 <- dummy_cols(data.raw4,select_columns="target",remove_first_dummy = TRUE)
colnames(yr70)[20] <- "year"
yr70$year[yr70$year == 0||yr70$year==1 ] <- '1970'

yr80 <- dummy_cols(data.raw5,select_columns="target",remove_first_dummy = TRUE)
colnames(yr80)[20] <- "year"
yr80$year[yr80$year == 0||yr80$year==1 ] <- '1980'

yr90 <- dummy_cols(data.raw6,select_columns="target",remove_first_dummy = TRUE)
colnames(yr90)[20] <- "year"
yr90$year[yr90$year == 0||yr90$year==1 ] <- '1990'

#Combine all data sorces together
data.yr <- ( rbind(yr00,yr10) %>% rbind(yr60) %>% rbind(yr70)
  %>% rbind(yr80) %>% rbind(yr90) )
```

```{r}
#Counting the energy and plot it over time
yearly_counts <- data.yr %>%
  count(year, energy)
ggplot(data = yearly_counts, aes(x = year, y = n, color = energy)) +
  ggtitle('Bar chart of energy level and its popularity over time')+
  geom_bar(stat='identity')
  
```
Now, we will see whether the trends persisted for tempo
```{r}
#Counting the energy and plot it over time
yearly_counts2 <- data.yr %>%
  count(year, tempo)
ggplot(data = yearly_counts2, aes(x = year, y = n, color = tempo)) +
  ggtitle('Bar chart of tempo level and its popularity over time')+
  geom_bar(stat='identity')
```

