---
title: "Spotify Hits Prediction"
output: html_notebook
---

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.


```{r}
set.seed(100)
curDir <- '/home/tinhc/Documents/GitHub/DataPrepProject'
setwd(curDir)
library(ggplot2)
library(tidyverse)
data.raw1 <- read.csv(file='dataset-of-00s.csv')
data.raw2 <- read.csv(file='dataset-of-10s.csv')
data.raw3 <- read.csv(file='dataset-of-60s.csv')
data.raw4 <- read.csv(file='dataset-of-70s.csv')
data.raw5 <- read.csv(file='dataset-of-80s.csv')
data.raw6 <- read.csv(file='dataset-of-90s.csv')

#Combine all data sorces together
data.raw <- ( rbind(data.raw1,data.raw2) %>% rbind(data.raw3) %>% rbind(data.raw4)
  %>% rbind(data.raw5) %>% rbind(data.raw6) )
```

```{r}
class(data.raw)
dim(data.raw)
str(data.raw)

#Check entire table for NA values
table(is.na(data.raw))
#See where NA values lies
colSums(is.na(data.raw))
#Omit NA values
data.raw1<-na.omit(data.raw)
#Get the summary of the dataset
summary(data.raw)
#Remove unnecessary columns
data.raw<-data.raw %>% select(-c(track,artist,uri))
```
Compute the correlation matrix

```{r}
library(ggcorrplot)
corr <- round(cor(data.raw),2)

#Calculate the corelation between p-value
pmat <- cor_pmat(data.raw)
head(pmat)

head(corr)
#Visualize the correlation matrix
ggcorrplot(corr)
#Reduce the correlation matrix to keep only lower half with hierarchical order
ggcorrplot(corr, hc.order = TRUE, type = "lower",
     outline.col = "white")
```
```{r}
# Add correlation significance level
# Check-mark the no significant coefficient features
ggcorrplot(corr, method='circle', hc.order = TRUE,
    type = "lower", p.mat = pmat)
```
Now, we will explore some of the key features against our target value
```{r}
ggplot(data=data.raw)+geom_histogram(aes(x=duration_ms,fill=energy,color = 'red'), binwidth  = 1000)
#ggplot(data.raw,aes(x=energy,y=target))+  geom_line()
```
